### 2018-07-24 experiments.tex
final mutation kill numbers

Non-differential testing, without failure determinism checks, killed
872 mutants, a 37.1\% kill rate.  Adding a failure determinism check
allowed the testing to kill an additional 98 mutants.
The differential harness, with an additional 60 seconds of testing
time, improved the kill rate to 49.4\%.  Failure determinism added an
additional 71 mutants to the total killed, even for this complete
harness with a larger test budget.  The kill rates are generally low
because {\tt universalmutator}, by design, includes many operations
that can produce equivalent mutants, but can also produce hard-to-kill
non-equivalent mutants not produced by other mutation tools, e.g. code
that throws away exceptions raised by a function call, or code
reversing a list.

>>>>

Non-differential testing, without failure determinism checks, killed
872 mutants, a 37.1\% kill rate.  Adding a failure determinism check
allowed the testing to kill an additional 98 mutants, an 11\% improvement.
The differential harness, with an additional 60 seconds of testing
time, killed 1148 mutants, improving the kill rate to 48.8\%.  Failure determinism added an
additional 71 mutants to the total killed, a 6\% improvement even for this complete
harness with a larger test budget.  The kill rates are generally low
because {\tt universalmutator}, by design, includes many operations
that can produce equivalent mutants, but can also produce hard-to-kill
non-equivalent mutants not produced by other mutation tools, e.g. code
that throws away exceptions raised by a function call, or code
reversing a list.
